STA610 Case Study 1 Team 4 Report

### 2021-03-21 STA 610 Case Study 1 Report_Team 4.Rmd
Added model selection for grouping variable

>>>>

First, let's decide what to group on for region:

```{r}
# Fit 3 models grouping on different location specificity
mod_s <- lmer(data=df, log_ppm ~ (1 |state) + date_num + date_quarter + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F)
print(paste("BIC for grouping on state", round(BIC(mod_s), 3)))

mod_c <- lmer(data=df, log_ppm ~ (1 |city) + date_num + date_quarter + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F)
print(paste("BIC for grouping on city", round(BIC(mod_c), 3)))

mod_r <- lmer(data=df, log_ppm ~ (1 |USA_region) + date_num + date_quarter + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F)
print(paste("BIC for grouping on region", round(BIC(mod_r), 3)))
```

State provides the best level of BIC, so we will choose this for our grouping variable.

Now let's investigate dropping various
